### 2015-05-31 writing/SNLI paper/entailment_eval.tex

% The table
\begin{table}
\begin{center}
\def\t#1{\small{#1}}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\b{System} & \b{Our corpus} & \b{SICK} & \b{RTE-3} \\
\hline
\t{Edit Distance Based}  & \t{71.9} & \t{65.4} & \t{64.4} \\
\t{Classifier Based}     & \t{72.2} & \t{74.3} & \t{65.3} \\
\hline
\t{Transformation Based} & \b{??.?} & \b{76.7} & \b{67.1} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
Accuracies of various entailment algorithms included in the
  Excitement Open Platform.
The edit distance and classifier based accuracies are are on a 2-class
  classification task; this results in a majority-class baseline
  of 66\% on our class and 71\% on SICK.
All RTE results are 2-class accuracy.
The transformation based model allows for 3-class predictions on our
  corpus and SICK; these are reported in the last row.
}
\end{table}
%
% END EOP RESULTS TABLE
%

% the best systems
We report results in \reftab{eopresults}, covering both our own test set,
  the SICK test data, and the standard RTE-3 test set \cite{giampiccolo2007third}.
Each of the models was trained on its own training set.
The results for RTE-3 are taken from \newcite{magnini2014excitement}.
The edit distance and classifier based models are evaluated only on
  2-class entailment; all RTE results are likewise reported for 2-class entailment.
To convert 3-class problems like SICK and our corpus to this setting, all instances
  of \contradiction\ and \unknown\ are converted to nonentailment.
This yields a chance baseline of 66\%.

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\b{System} & \b{Train}  & \b{Test} \\ % \t{Dev}
\hline
\t{Lexicalized}            & \t{99.7} 	& \b{78.2} \\ % & \t{78.7} 
\t{Unigrams Only}          & \t{93.1} & \t{71.6} \\ % & \t{72.2} 
\t{Unlexicalized}          & \t{49.4} 	 & \t{50.39} \\ % & \t{50.1} 
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
Accuracy on the our dataset, including precision/recall for the
  \textit{entailment} class on the test set.
Ablation results are reported for models lacking cross-bigram features 
  (Feature \ref{lst:bigram}), and lacking all lexical
  features (Features \ref{lst:ngram}--\ref{lst:bigram}).
}
\end{table}
%
% END BOW RESULTS TABLE
%

% Results
We report results in \reftab{bowresults}, along with ablation studies for removing
  the bigram features (leaving only the unigram entailment pair feature),
  and for removing all lexicalized features.

@@

% \t{100d TreeRNN}            & \t{69?} & \t{69?} \\
% \t{50d TreeRNTN}            & \t{61?} & \t{60?} \\
% \t{100d LSTM TreeRNN}            & \t{72?} & \t{73?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy in 3-class classification on our training and test sets for each model.
}
\end{table}

The results are shown in Table~\ref{tab:nnresults}. The sum of words model performed slightly worse than the fundamentally similar lexicalized classifier---while the sum of words model is able to use pretrained word embeddings to better handle rare words, it lacks even the rudimentary sensitivity to word order that the lexicalized model's bigram features provide. Of the two RNN models, the LSTM's more robust ability to learn long-term dependencies serves it well, giving it a substantial advantage over the plain RNN, and  resulting in performance that is essentially equivalent to the lexicalized classifier.

@@

Figure \ref{fig:bowlearncurve} shows a learning curve for the LSTM and the lexicalized and unlexicalized feature-based models. This learning curve shows that the large size of the corpus is crucial to both the LSTM and the lexicalized model, and suggests that additional data would yield still better performance for both. In addition, though the LSTM and the lexicalized model show similar performance when trained on the current full corpus, the steeper slope for the LSTM suggests that its ability to learn arbitrarily structured representations of sentence meaning would give it an advantage over the more constrained lexicalized model on still larger datasets.

>>>>

% The table
\begin{table}
\begin{center}
\def\t#1{\small{#1}}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\toprule
\b{System} & \b{Our corpus} & \b{SICK} & \b{RTE-3} \\
\midrule
\t{Edit Distance Based}  & \t{71.9} & \t{65.4} & \t{64.4} \\
\t{Classifier Based}     & \t{72.2} & \t{74.3} & \t{65.3} \\
\midrule
\t{Transformation Based} & \b{??.?} & \b{76.7} & \b{67.1} \\
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
Accuracies of various entailment algorithms included in the
  Excitement Open Platform.
The edit distance and classifier based accuracies are are on a 2-class
  classification task; this results in a majority-class baseline
  of 66\% on our class and 71\% on SICK.
All RTE results are 2-class accuracy.
The transformation based model allows for 3-class predictions on our
  corpus and SICK; these are reported in the last row.
}
\end{table}
%
% END EOP RESULTS TABLE
%

% the best systems
We report results in \reftab{tab:eopresults}, covering both our own test set,
  the SICK test data, and the standard RTE-3 test set \cite{giampiccolo2007third}.
Each of the models was trained on its own training set.
The results for RTE-3 are taken from \newcite{magnini2014excitement}.
The edit distance and classifier based models are evaluated only on
  2-class entailment; all RTE results are likewise reported for 2-class entailment.
To convert 3-class problems like SICK and our corpus to this setting, all instances
  of \contradiction\ and \unknown\ are converted to nonentailment.
This yields a chance baseline of 66\%.

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\toprule
\b{System} & \b{Train} & \b{Test} \\
\midrule
\t{Lexicalized}            & \t{99.7}  & \b{78.2} \\ % & \t{78.7}
\t{Unigrams Only}          & \t{93.1} & \t{71.6} \\ % & \t{72.2}
\t{Unlexicalized}          & \t{49.4} & \t{50.4} \\ % & \t{50.1} % Last value was 50.39; rounded for consistency.
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
Accuracy on the our dataset, including precision/recall for the
  \textit{entailment} class on the test set.
Ablation results are reported for models lacking cross-bigram features 
  (Feature \ref{lst:bigram}), and lacking all lexical
  features (Features \ref{lst:ngram}--\ref{lst:bigram}).
}
\end{table}
%
% END BOW RESULTS TABLE
%

% Results
We report results in \reftab{tab:bowresults}, along with ablation studies for removing
  the bigram features (leaving only the unigram entailment pair feature),
  and for removing all lexicalized features.

@@

% \t{100d TreeRNN}            & \t{69?} & \t{69?} \\
% \t{50d TreeRNTN}            & \t{61?} & \t{60?} \\
% \t{100d LSTM TreeRNN}            & \t{72?} & \t{73?} \\
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy in 3-class classification on our training and test sets for each model.
}
\end{table}

The results are shown in \reftab{tab:nnresults}. The sum of words model performed slightly worse than the fundamentally similar lexicalized classifier---while the sum of words model is able to use pretrained word embeddings to better handle rare words, it lacks even the rudimentary sensitivity to word order that the lexicalized model's bigram features provide. Of the two RNN models, the LSTM's more robust ability to learn long-term dependencies serves it well, giving it a substantial advantage over the plain RNN, and  resulting in performance that is essentially equivalent to the lexicalized classifier.

@@

\Reffig{fig:bowlearncurve} shows a learning curve for the LSTM and the lexicalized and unlexicalized feature-based models. This learning curve shows that the large size of the corpus is crucial to both the LSTM and the lexicalized model, and suggests that additional data would yield still better performance for both. In addition, though the LSTM and the lexicalized model show similar performance when trained on the current full corpus, the steeper slope for the LSTM suggests that its ability to learn arbitrarily structured representations of sentence meaning would give it an advantage over the more constrained lexicalized model on still larger datasets.
